Draft Research pt1

### 2019-03-02 draftResearch_pt1.Rmd
Encapsulated a single JSON example

players_list %>% rlist::list.stack()

players %>% list.load()

```

>>>>

# trying different approach from https://cran.r-project.org/web/packages/jsonlite/vignettes/json-aaquickstart.html
players %>%
  content("text") %>%
  fromJSON() -> players_fromJSON

players_fromJSON$fantasy_content$users$`0`$user$games$`0`$game[[2]]$players[1:25] -> players_fromJSON_dataframe

players_fromJSON_dataframe$`0`$player[[2]][[1]]

# data camp approach
players_content$fantasy_content$users$`0`$user[[2]]$games$`0`$game[[2]][[1]] -> players_content_list

players_content_list %>% str(max.level=3)
players_content_list %>% saveRDS("data/players_content_list.Rds")
```
So this is a list of 26 elements, 25 lists, and "count" int = 25. One player is represented in each of the 25 nested lists, but their data is actually three levels of nesting beneath!

Need to figure out how to extract that great-grandchild list from each of the 25 child lists, then I should be able to stack them via rlist.
